### 2019-11-14 Mathematical Statatistics/ms_ch_02.rmd
mathematical statistics ch2 work
mathematical statistics ch2 work
mathematical statistics, ch2 work
mathematical statistics, ch2 work

Let $w_i = x_i + y_i$ for i = 1, 2, ..., n.

@@

@@

>>>>

Let $w_i = x_i + y_i$ for $i = 1, 2, \ldots, n$.

@@

\setlength{\leftskip}{2cm}

$\bar{w} = \bar{x} + \bar{y} = \frac{1}{n}\sum_{i=1}^{n}x_n + \frac{1}{n}\sum_{i=1}^{n}y_n$

$\ldots = \frac{1}{n}\sum_{i=1}^{n}[x_n + y_n]$

\setlength{\leftskip}{0pt}

@@

\setlength{\leftskip}{2cm}

$m_x = \frac{x_{[(\#x+1)\div2]} + x_{[(\#x+1)\div2]}}{2}$

$m_y = \frac{y_{[(\#y+1)\div2]} + y_{[(\#y+1)\div2]}}{2}$

$m_x + m_y = \frac{x_{[(\#x+1)\div2]} + x_{[(\#x+1)\div2]}}{2} + \frac{y_{[(\#y+1)\div2]} + y_{[(\#y+1)\div2]}}{2}$

$\ldots = \frac{1}{2}(x_{[(\#x+1)\div2]} + x_{[(\#x+1)\div2]} + y_{[(\#y+1)\div2]} + y_{[(\#y+1)\div2]})$

\setlength{\leftskip}{0pt}

### 2.10

Find the median __m__ and first and third quartiles for the random variable $X$ having:

a.) The exponential distribution with $pdf f(x) = \lambda e^{-\lambda x}$

\setlength{\leftskip}{2cm}

__m__ = $\frac{ln(2)}{\lambda}$ =

$q_p = -\frac{ln(1 - p)}{\lambda}$, where q in .25, .5, .75.

\setlength{\leftskip}{0cm}

b.) The Pareto distribution with parameter $\alpha > 0$ with $pdf f(x) = \frac{\alpha}{X^{\alpha+1}}$

### 2.11

Let the random variable X have a Cauchy distribution with $pdf f(x) = \frac{1}{\pi(1 + x(x - \theta)^2))}$ for $-\infty < x < \infty$.

a.) Show that the mean of X does not exist.

b.) More generally, will $\mathbb{E}[X^k]$ exist? (k = 1, 2, 3, ...).

c.) Show that $\theta$ is the median of the distribution.
